### 2023-06-22 manuscript.tex
arxiv [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/251c1d7a7c7a10ef9206e0a11ed9bb3d24dcf8b1.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/251c1d7a7c7a10ef9206e0a11ed9bb3d24dcf8b1/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5340408964

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/b1393612506612279d1adce2c9bc387fde40c48f/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/b1393612506612279d1adce2c9bc387fde40c48f}{stain/2022-fdo-paper@b139361}
on June 22, 2023.

>>>>

\emph{An updated preprint of this manuscript is available at \url{https://doi.org/10.48550/arXiv.2306.07436}
-- these pages may not reflect the latest changes.}.

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/251c1d7a7c7a10ef9206e0a11ed9bb3d24dcf8b1/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/251c1d7a7c7a10ef9206e0a11ed9bb3d24dcf8b1}{stain/2022-fdo-paper@251c1d7}
on June 22, 2023.
